---
title: "STACYtsplot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

This markdown helps you to construct STACYtsplots, which combine timeseries plots for multiple proxy, forcing, and simulation data. The following steps are included:
1) Load packages
2) Import data
3) Plot configuration
4) Step-by-step plotting [Needs to be in 1 chunk to plot to the same device]

## 1) Load packages

First we load several necessary packages:

```{r packages,warning=FALSE,message=FALSE}

library(zoo)
library(TeachingDemos)
library(nest)
library(ncdf4)

```


## 2) Import data

Next, proxy, forcing, and simulation data is imported. Feel free to add (and describe) new data.

```{r import,warning=FALSE,message=FALSE}
# Load data
load("/home/ronweasley/Data/timeseries_deglac_comp.RData")
load("/home/ronweasley/Data/full_image_fig1_proposal.RData")

# PROXY DATA
# NGRIP d18O
ngrip <- TS$ngrip
# EPICA d18O
epica <- prxlist[[107]]
# Sihailongwan arboreal pollen (unpublished!)
load("/stacydata/data/squirrel/pollen/Sihailongwan/glacial_shl/data/moderndata.RData")
pollen_tmp <- read.csv("/home/ronweasley/Data/SHLpollen.csv",header=TRUE,sep=";")
ap <- pollen_tmp$AP
ap <- ap[-which(is.na(ap))]
nap <- pollen_tmp$NAP
nap <- nap[-which(is.na(nap))]
new_age <- pollen_tmp$age..neu.
new_age <- new_age[-which(is.na(new_age))]
#6 elements with non-unique ages: 380:384, 642:644
ap[380] <- mean(ap[380:384]); ap[642] <- mean(ap[642:644])
nap[380] <- mean(nap[380:384]); nap[642] <- mean(nap[642:644])
ap <- ap[-c(381:384,643:644)]; nap <- nap[-c(381:384,643:644)]

# SIMULATION DATA
# BBC HadCM3
sim_names <- paste(read.csv("/stacydata/data/BRIDGE/BRIDGE.csv",header=TRUE)$bbc_all_triff_rev_dyn04)[1:62]
sim_dates <- c(seq(120,80,by=-4),seq(78,22,by=-2),seq(21,0,by=-1))
nc <- nc_open("/stacywork/ronweasley/tmp/bridge_mean_ts.nc")
bridge_ts <- ncvar_get(nc,"TS")
bridge_time <- sim_dates
# FAMOUS
nc <- nc_open("/stacydata/data/FAMOUS/glacial_cycle/ALL-5G_24.cdf")
famous_time <- ncvar_get(nc,"time")
nc <- nc_open("/stacywork/ronweasley/tmp/famous_mean_ts.nc")
famous_ts <- ncvar_get(nc,"surface_temperature")
# LOVECLIM
# TraCE-21ka
nc <- nc_open("/stacydata/data/trace21ka/trace.01-36.22000BP.cam2.TS.22000BP_decavg_400BCE.nc")
trace_time <- ncvar_get(nc,"time")
nc <- nc_open("/stacywork/ronweasley/tmp/trace_mean_ts.nc")
trace_ts <- ncvar_get(nc,"TS")

# FORCING DATA
# Summer insolation
# Seasonality
# CO2
co2 <- TS$co2_orig_smooth
co2 <- rev.zoo(co2)
index(co2) <- sort(-index(co2))
# Solar forcing

# EVENTS
# Marine isotope stages
mis_transitions <- -MIS.trans
# Holocene
# LGM
# Heinrich stadial events
# Old:
h_events <- HE.t # Before DO4, DO8, DO12, DO17
# New (from Collins 2013, based on AICC2012)
# 1  (15–18.5 ka),  2  (23.5–25.5 ka),  3(29–30.5 ka),  4  (38.5–40 ka)  and  5  (47–48.5 ka)
hs_events <- t(array(c(15,18.5,23.5,25.5,29,30.5,38.5,40,47,48.5,60,61),dim=c(2,6)))
hs_mid_points <- apply(hs_events,1,mean)
# Greenland interstadials (DO events)
gis_onsets <- Dtab$Age.ka.b.1950*1000
gis_duration <-c(1,19,1,3,3,5,4,7,16,3,7,10,26,1,1,1,1,1,3,20,24)*100
# Corrections
gis_duration_new <- gis_duration
gis_duration_new[14] <- 1000; gis_duration_new[15] <- 4700; gis_duration_new[16] <- 400; gis_duration_new[17] <- 1800; gis_duration_new[18] <- 800
gis_onsets[22] <- 84200; gis_duration_new[22] <- 7000
gis_onsets[23] <- 89500; gis_duration_new[23] <- 2400
# Onset of Dansgaard-Oescher events
do_event_onsets <- -DO.t
# NGRIP temperature jumps in DO events, in [K]
ngrip_do_temp_diff <- c(10.5,12.5,8.5,14.5,12.5,12.5,9.5,15.5,10,6.5,13.5,16.5,12.5,8.5,12.5,10,10,12.5,13.5,14,12.5,13.5)
# Common era events?

#/stacydata/squirrel/HollgmVar2020

```

## 3) Configure plot

Then, we configure the plot by specifying age limits, the number of combined timeseries plots, colors of the timeseries, and font sizes. Feel free to add new color definitions for new timeseries.

```{r configuration,warning=FALSE,message=FALSE}

# Age limits
xlimz<-c(-67000,500)

# Number of timeseries in the plot
num_ts <- 4
# Set layout:

# Set standard colors for the timeseries
col_shl <- "darkgreen"
col_famous <- "red3"
col_bridge <- "brown"
col_trace <- "orangered2"#"slategray"
col_ngrip <- "black"
col_epica <- "blue"
col_co2 <- "orangered2"
col_model <- "blue4"
col_proxy <- "red3"
col_hadcm3 <- "modelcolr"
col_echam <- "dodgerblue"
col_sealevel <-"slategray"
col_insolation <- "springgreen4"
col_txt <- "darkslategray"

# Settings for size of axes, units, and names
axisnumscex <- 1.5 #0.75
axslinno <- 1.5 #0.75
unitscex <- 1.5 #0.75
unitslinno <- 6 #2.5
namlin <- 1 #0.5
namcex <- 1.75 #1

```

## 4) Step-by-step plotting

Finally the plot is created step by step. Here, you need to add new code paragraphs for new datasets.

```{r plotting,warning=FALSE,message=FALSE}
#Start graphics device
#Vector graphic:
cairo_pdf(width=12,height=8,file="/home/ronweasley/Plots/timeseries_example.pdf")
# Raster graphic:
#png(width=12,height=8,units = "cm",file=paste(outputdir,"/Fig1_talk.png",sep=""),res=150)

# Set margins, out margin, axes styles, standard text size, and line width
par(mar=c(0,0,0,0),oma=c(2,19,6,21),xaxs="i",yaxs="i",cex=1,lwd=2)

# The first row denotes the header (e.g. names of geologic periods), the remaining rows correspond to the individual timeseries plots
layout(matrix(rep(1:(num_ts+1),each=2),num_ts+1,2,byrow=TRUE),heights=c(0.2,1,1,1,1))

#HEADER
# Start plot
plot(xlimz,c(0,1),axes=FALSE,type="n",xlab="",ylab="")
# Lines to mark Holocene and LGM
arrows(x0=0,x1=-11300,y0=0.01,y1=0.01,code=3,angle=90,length=0.025,col=txtcol)
arrows(x0=-19000,x1=-27000,y0=0.01,y1=0.01,code=3,angle=90,length=0.025,col=txtcol)
# Text for MIS3, Holocene, and LGM
text(MIS.t[3],rep(0.5,length(MIS.t[3])),MIS.n[3],col=txtcol,cex=1.5*namcex)
text(mean(c(-12300,0)),0.5,"Holocene",col=txtcol,cex=1.5*namcex)
text(mean(c(-27000,-19000)),0.5,"LGM",col=txtcol,cex=1.5*namcex)
# Add top axis
mtext(side=3,line=3.25,"time [kyrs BP]",cex=unitscex)
tmp.y <- cnvrt.coords(x=NA,y=par('usr')[4])$dev$y
axis(3,at=seq(-60,0,by=10)*1000,labels=FALSE);
mtext(side=3,at=seq(-60,0,by=10)*1000,seq(60,0,by=-10),line=0.5,cex=axisnumscex)

#SHL
# y-axis extent:
range_shl <- c(0,100)
# Start plot
plot(xlimz,range_shl,axes=FALSE,type="n",xlab="",ylab="")
# Add full and filtered timeseries
lines(-rev(foss.time),rev(ap),type="l",col=adjustcolor(col_shl,0.3))
lines(-rev(foss.time),gaussdetr(zoo(rev(ap),order.by=-rev(foss.time)),tsc.in=2000)$Xsmooth,type="l",col=col_shl)
# Add proxy name (on left side)
mtext(side=2,expression(paste(plain(Sihailongwan)," ",plain(AP))),cex=namcex,line=namlin,las=1,col=col_shl)
# Add units (on right side)
mtext(side=4,"[%]",line=unitslinno,cex=unitscex,las=1,col=col_shl)
# Add axis (on right side)
axis(4,at=seq(0,100,by=25),labels=FALSE,col=col_shl)
mtext(side=4,at=seq(0,100,by=25),seq(0,100,by=25),line=axslinno,las=1,cex=axisnumscex,col=col_shl)

#EPICA
epica <- zoo(rev(epica),order.by = -rev(index(epica)))
rgepica<-range(epica[which(index(epica) <= 0 & index(epica) >= -67000)])
plot(xlimz,rgepica,axes=FALSE,type="n",xlab="",ylab="")
lines(epica,col=adjustcolor(col_epica,0.3))
lines(gaussdetr(epica,tsc.in=2000)$Xsmooth,col=col_epica)
xtkz <-axTicks(2)[seq(1,by=2,length(axTicks(2))-1)]
axis(2,col=col_epica,at=xtkz,labels=FALSE)
mtext(side=2,col=col_epica,at=xtkz,xtkz,line=axslinno,las=1,cex=axisnumscex)
#mtext(side=2,expression(paste("\u0394",bgroup("[","\u2030" ,"]"))),cex=unitscex,col="black",line=unitslinno,las=1)
mtext(side=2,expression(paste("[",delta^{plain(18)}, plain(O),"]")),cex=unitscex,col=col_epica,line=unitslinno,las=1)
mtext(side=4,expression(plain(EPICA)^{12}),cex=namcex,col=col_epica,line=namlin,las=1)

#NGRIP
rgngrp<-range(ngrip[which(index(ngrip) <= 0 & index(ngrip) >= -67000)])
plot(xlimz,rgngrp,axes=FALSE,type="n",xlab="",ylab="")
lines(ngrip,col=adjustcolor(col_ngrip,0.3))
lines(gaussdetr(ngrip,tsc.in=2000)$Xsmooth,col=col_ngrip)
xtkz <-axTicks(2)[seq(1,by=2,length(axTicks(2))-1)]
axis(4,col=col_ngrip,at=xtkz,labels=FALSE)
mtext(side=4,col=col_ngrip,at=xtkz,xtkz,line=axslinno,las=1,cex=axisnumscex)
mtext(side=4,expression(paste("[",delta^{plain(18)}, plain(O),"]")),cex=unitscex,col=col_ngrip,line=unitslinno,las=1)
mtext(side=2,expression(plain(NGRIP)^{11}),cex=namcex,col="black",line=namlin,las=1)

#SIMULATIONS
tlims <- c(-6.5,0.5)#range(famous_ts-famous_ts[which.min(abs(famous_time))],trace_ts-trace_ts[which.min(abs(trace_time))],bridge_ts-bridge_ts[which.min(abs(bridge_time))],na.rm=TRUE)
plot(xlimz,tlims,axes=FALSE,type="n",xlab="",ylab="")
lines(famous_time*10,famous_ts-famous_ts[which.min(abs(famous_time))],type="l",ylim=c(-6.5,0.5),col=adjustcolor(col_famous,0.3))
lines(trace_time*1000,trace_ts-trace_ts[which.min(abs(trace_time))],type="l",col=adjustcolor(col_trace,0.3))
lines(famous_time*10,gaussdetr(zoo(famous_ts-famous_ts[which.min(abs(famous_time))],order.by=famous_time*10),tsc.in=2000)$Xsmooth,type="l",ylim=c(-6.5,0.5),xlim=c(-66,0),col=col_famous)
lines(trace_time*1000,gaussdetr(zoo(trace_ts-trace_ts[which.min(abs(trace_time))],order.by=trace_time*1000),tsc.in=2000)$Xsmooth,type="l",col=col_trace)
lines(-bridge_time*1000,bridge_ts-bridge_ts[which.min(abs(bridge_time))],type="l",col=col_bridge)
units$tanom<-expression(bgroup("[", paste("",{}^{o}, plain(C)),"]"))
mtext(side=2,units$tanom,line=unitslinno,cex=unitscex,las=1)
axis(2,at=seq(-6,0,by=2),labels=FALSE);
mtext(side=2,at=seq(-6,0,by=2),seq(-6,0,by=2),line=axslinno,las=1,cex=axisnumscex)
mtext(side=4,expression(paste(plain(Global)," ",plain(temperature))),cex=namcex,col="black",line=namlin,las=1,padj=-1)
mtext(side=4,expression("HadCM3"),cex=namcex,col=col_bridge,line=namlin,las=1,padj=0)
mtext(side=4,expression("TraCE-21ka"),cex=namcex,col=col_trace,line=namlin,las=1,padj=1.5)
mtext(side=4,expression("FAMOUS"),cex=namcex,col=col_famous,line=namlin,las=1,padj=3)

#FORCINGS

par(xpd=NA)
tmp.y2 <- cnvrt.coords(x=NA, y=tmp.y, input='dev')$usr$y
segments(c(min(xlimz),max(xlimz),min(xlimz),min(xlimz)),c(par('usr')[3],par('usr')[3],par('usr')[3],tmp.y2),c(par('usr')[1],par('usr')[2],max(xlimz),max(xlimz)),c(tmp.y2,tmp.y2,par('usr')[3],tmp.y2))
segments(x0=MIS.trans[2:4],x1=MIS.trans[2:4],y1=par('usr')[3],y0=1*tmp.y2,lty=2,col="grey")

dev.off()


```



